A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer

### 2024-01-26 content/manuscript.qmd
run, produce prev plots & track SVGs

  model manages to cluster anatomically close subsites and correctly infers the

@@

We did this in this and that fashion...

>>>>

  model manages to group anatomically close subsites and correctly infers the

@@

In our implementation of the EM alorithm, we alternated between the following two steps:

1. Given a set of $\boldsymbol{\pi}^\star$, we sampled new cluster parameters $\boldsymbol{\theta}^\star$ from the . we ran 7 times {{< var mixture_model.em_config.e_step.walkers_per_dim >}} parallel `emcee` walkers for  {{< var mixture_model.em_config.e_step.nburnin >}} steps and discarded the results as burn-in. Then, we completed another {{< var mixture_model.em_config.e_step.nsteps >}} steps and used
